---
title: "India's Socio-Economic Landscape"
author: "Ayush Patel"
date: "September 22, 2023"
subtitle: "Post Independence changes in India"
format: 
  revealjs:
    embed-resources: true
    slide-number: c/t
    width: 1400
    theme: [serif, theme.scss]
execute: 
  echo: false
  warning: false
---


```{r libraries}
library(here) # directories management
library(dplyr) # data wrangling
library(tidyr) # data wrangling
library(highcharter) # interactive data viz

```

```{r load-data}
# read in WB data that is processed and combined.
readr::read_csv(
  "data/WB_socio_economic_inds.csv"
) -> wb_all_ind

# transform WB data in long format.

wb_all_ind[,-c(1,69)]|> 
  pivot_longer(cols = 5:67,
               names_to = "year",
               values_to = "val")|>
  mutate(
    year = as.numeric(year)
  )-> wb_all_ind

# create a vector for comparative countries

names_neighbours_iso3c <- c("BGD","PAK","IND",
                            "CHN","KOR","LKA")

```


## Hello

::::{.columns}

:::{.column width="70%"}
[I am Ayush.]{.fragment fragment-index="1" style="font-size:45px"}


[I am a researcher working at the intersection of data, law, development and economics.]{.fragment fragment-index="2" style="font-size:25px"} 

[I teach Data Science using R at Gokhale Institute of Politics and Economics.]{.fragment fragment-index="3" style="font-size:25px"} 

[I am a [RStudio (Posit) certified tidyverse Instructor.](https://education.rstudio.com/trainers/people/patel+ayush/)]{.fragment fragment-index="4" style="font-size:25px"} 

[I am a Researcher at [Oxford Poverty and Human development Initiative (OPHI)](https://ophi.org.uk/), at the University of Oxford.]{.fragment fragment-index="5" style="font-size:25px"} 
:::

:::{.column width="30%"}

__Reach me__

{{< fa solid envelope >}} [ayush.ap58@gmail.com]{style="font-size:25px"}

{{< fa solid envelope >}} [ayush.patel@gipe.ac.in]{style="font-size:25px"}

:::

::::

## A liberal Constitution

[India adopted liberal constitution that came into force on 26 January 1950.]{.fragment fragment-index="1"}

[   - Universal Adult Franchise.]{.fragment fragment-index="2"}

[   - Equality based on caste, creed and religion]{.fragment fragment-index="3"}

[   - Freedom of speech and movement]{.fragment fragment-index="4"}

[   - Directive Principles of State Policy]{.fragment fragment-index="5"}

[   - Independent Judiciary]{.fragment fragment-index="6"}

>[One could say a right recipe for a harmonious society and growth. We will discuss how Indians and Indian society have changed after independence.]{.fragment fragment-index="7"}

## How are we measuring change?

  - **Education** and **Health**, of various groups, are two broad parameters that signal about a society's wellbeing. Additionally, are also signals for a productive and value generating labour force.
  - We will compare India, using various indicators^[form world bank data], with sub-continental neighbours.
  - We will also investigate, by discussing two papers from [Development Data Lab](https://www.devdatalab.org/), if change has been true for various groups in India.

## Where does India live?

>"India lives in her villages" - M.K. Gandhi

  - How much does this hold true today?
  - Is Urbanization desirable?
  - Has India Urbanized?
  
> "What is the village but a sink of localism, a den of ignorance, narrow-mindedness and communalism..." - B.R.Ambedkar

## Where does India Live?

```{r pop-changes}

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Rural population (% of total population)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Rural population (% of total population)`,
               name = paste("Rural population (% of total population)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Share of Rural Population"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of total population"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> sahre_rural_pop

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Urban population (% of total population)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Urban population (% of total population)`,
               name = paste("Urban population (% of total population)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Share of Urban Population"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of total population"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> sahre_urban_pop

```

:::{.panel-tabset}

### Rural

```{r}
#| fig-height: 6
#| fig-width: 14
sahre_rural_pop
```


### Urban

```{r}
#| fig-height: 6
#| fig-width: 14
sahre_urban_pop
```


:::

## Is India an agrarian economy?{.center}

  - Yes, India was an agrarian economy. Agri,forestry and fishing(1960)-41.7%GDP, Manufacturing(1960)-15%GDP and, Services(1960) - 38.8%GDP.
  - *Is* India an agrarian economy? Difficult to say. Things have changed(Agri,forestry and fishing(2022)-16.6%GDP, Manufacturing(2022)-13%GDP and, Services(2022) - 48.6%GDP).
  - Certainly, not same as 1960s. Is the change universal? Today, how many people are engaged in agriculture?
  
## Is India an agrarian economy?

```{r engaged-agri}
wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Agricultural land (sq. km)"
    )
  )|>
  filter(`Country Code` %in% c("IND","CHN"))|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Agricultural land (sq. km)`,
               name = paste("Agricultural land (sq. km)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Changes in Agriculture Land (sq. Km.)"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "Land in Square Kilometers"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> agri_land_sqm

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Arable land (hectares per person)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Arable land (hectares per person)`,
               name = paste("Arable land (hectares per person)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Arable land (hectares per person)"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "Hectares per person"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> land_per_person

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Agricultural irrigated land (% of total agricultural land)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Agricultural irrigated land (% of total agricultural land)`,
               name = paste("Agricultural irrigated land (% of total agricultural land)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Agricultural irrigated land"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of total agricultural land"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> irrigated_land

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Employment in agriculture (% of total employment) (modeled ILO estimate)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Employment in agriculture (% of total employment) (modeled ILO estimate)`,
               name = paste("Employment in agriculture (% of total employment) (modeled ILO estimate)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Employment in agriculture(modeled ILO estimate)"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of total employment"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> agri_employed

```

:::{.panel-tabset}

### Land resource

```{r}
#| fig-height: 6
#| fig-width: 14

agri_land_sqm
```


### Per Capita

```{r}
#| fig-height: 6
#| fig-width: 14

land_per_person
```

### Irrigated land

```{r}
#| fig-height: 6
#| fig-width: 14

irrigated_land
```

### Labour in Agri

```{r}
#| fig-height: 6
#| fig-width: 14

agri_employed
```

:::

## Inefficiencies in Agriculture

  - Today for India, nearly 43% of the total employment is in Agriculture. Even though, value added by agriculture to GDP is ~16%.
  - China, that has a comparable population to India, requires a little more than 3 times the area of agriculture land to support itself. This is despite the fact that yield per hectare in China is higher compared to India^[[see1](https://ageconsearch.umn.edu/record/7510/files/edc87-03.pdf),[see2](https://www.nationmaster.com/country-info/compare/China/India/Agriculture),[see3](https://www.cambridge.org/core/journals/journal-of-asian-studies/article/abs/chinese-and-indian-agriculture-a-broad-comparison-of-recent-policy-and-performance/49317DFE78554C23AC3467F604AF009B)].
  - India has a lower share of irrigated land compared to Bangladesh and Pakistan.
  

## Labour Force{.center}

  - Does being a populous and young country help?
  - What is the employment share outside agriculture?
  - Are women participating in the work force?
  
## Labour Force

```{r charts-labour}


wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Employment in agriculture, female (% of female employment) (modeled ILO estimate)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Employment in agriculture, female (% of female employment) (modeled ILO estimate)`,
               name = paste("Employment in agriculture, female (% of female employment) (modeled ILO estimate)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Female Participation in Agriculture"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of total female employment"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> agri_female


wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Labor force, total"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Labor force, total`,
               name = paste("Labor force, total",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Total Labour Force"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "Number of People"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> labour_force


wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Labor force, female (% of total labor force)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Labor force, female (% of total labor force)`,
               name = paste("Labor force, female (% of total labor force)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Female Labour Force Participation"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of total labour force"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> labour_force_female



wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Wage and salaried workers, female (% of female employment) (modeled ILO estimate)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Wage and salaried workers, female (% of female employment) (modeled ILO estimate)`,
               name = paste("Wage and salaried workers, female (% of female employment) (modeled ILO estimate)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Wage and Salaired Female Workers"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of female employment"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> wage_salary_female_worker


wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Age dependency ratio (% of working-age population)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Age dependency ratio (% of working-age population)`,
               name = paste("Age dependency ratio (% of working-age population)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Age Dependency Ratio"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of working age population"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> age_dependency

```

:::{.panel-tabset}

### Labour Force

```{r}
#| fig-height: 6
#| fig-width: 14

labour_force
```


### In Agri

```{r}
#| fig-height: 6
#| fig-width: 14

agri_employed
```

### Age Dependency
```{r}
#| fig-height: 6
#| fig-width: 14

age_dependency
```

:::

## Labour force

:::{.panel-tabset}

### Female-LFP
```{r}
#| fig-height: 6
#| fig-width: 14

labour_force_female
```
### Female in Agri
```{r}
#| fig-height: 6
#| fig-width: 14

agri_female
```

### Wage and Salaried
```{r}
#| fig-height: 6
#| fig-width: 14

wage_salary_female_worker
```


:::

## Electricity{.center}

  - Why special focus on Electricity?
  - One of the primary inputs required for any economic activity.
  - Also a signal for standard of living.
  - Important factors to consider given climate change.

*We will explore access to electricity, Per capita power consumption, and renewable electricity output.*

## Electricity

```{r charts-ele}


wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Access to electricity (% of population)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Access to electricity (% of population)`,
               name = paste("Access to electricity (% of population)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Access to Electricity - National"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of total population"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> access_naitonal


wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Access to electricity, rural (% of rural population)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Access to electricity, rural (% of rural population)`,
               name = paste("Access to electricity, rural (% of rural population)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Access to Electricity - Rural"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of total population"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> access_rural


wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Electric power consumption (kWh per capita)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Electric power consumption (kWh per capita)`,
               name = paste("Electric power consumption (kWh per capita)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Electric power consumption per capita"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "KWh per capita"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> ele_consumption_per_head


wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Renewable electricity output (% of total electricity output)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Renewable electricity output (% of total electricity output)`,
               name = paste("Renewable electricity output (% of total electricity output)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Renewable electricity output"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of total electricity output"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> renew_output

```

:::{.panel-tabset}

### National

```{r}
#| fig-height: 6
#| fig-width: 14

access_naitonal
```

### Rural

```{r}
#| fig-height: 6
#| fig-width: 14

access_rural
```

### Consumption

```{r}
#| fig-height: 6
#| fig-width: 14

ele_consumption_per_head
```

### Renewable Output

```{r}
#| fig-height: 6
#| fig-width: 14

renew_output
```

:::

## Health{.center}

   - Studies show relation between nutrition  intake and growth.^[[see1](https://www.fao.org/3/ae030t/ae030t.pdf),[see2](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1839860/#:~:text=Links%20between%20nutrition%20and%20economic,rates%20declined%20by%20~5%25.)]
   - Health of labour force has implications for economy.
   - There is intrinsic value in having good health indicators.
   - Signals welfare functioning of the state.
   
## Health 

```{r health-charts1}
wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Current health expenditure per capita, PPP (current international $)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Current health expenditure per capita, PPP (current international $)`,
               name = paste("Current health expenditure per capita, PPP (current international $)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Health Expenditure Per capita"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "PPP (Current International $)"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> exp_health


wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Life expectancy at birth, total (years)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Life expectancy at birth, total (years)`,
               name = paste("Life expectancy at birth, total (years)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Life expectancy at birth"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "Years (total)"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> life_years

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Birth rate, crude (per 1,000 people)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Birth rate, crude (per 1,000 people)`,
               name = paste("Birth rate, crude (per 1,000 people)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Birth rate, crude (per 1,000 people)"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "Number per 1000 people"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> birth_rate

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Fertility rate, total (births per woman)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Fertility rate, total (births per woman)`,
               name = paste("Fertility rate, total (births per woman)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Fertility rate, total"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "Births per woman"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> fert_rate

```

:::{.panel-tabset}

### Expenditure
```{r}
#| fig-height: 6
#| fig-width: 14 

exp_health
```

### Life Expectancy
```{r}
#| fig-height: 6
#| fig-width: 14 

life_years
```
### Birth Rate
```{r}
#| fig-height: 6
#| fig-width: 14 

birth_rate
```
### Fertility
```{r}
#| fig-height: 6
#| fig-width: 14 

fert_rate
```

:::
   
## Health

```{r health-charts2}

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Prevalence of anemia among non-pregnant women (% of women ages 15-49)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Prevalence of anemia among non-pregnant women (% of women ages 15-49)`,
               name = paste("Prevalence of anemia among non-pregnant women (% of women ages 15-49)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Anemia among non-pregnant women (age 15-49)"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of women between 15-49"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> anemia_w

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Prevalence of anemia among pregnant women (%)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Prevalence of anemia among pregnant women (%)`,
               name = paste("Prevalence of anemia among pregnant women (%)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Anemia among pregnant women"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of pregnant women"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> anemia_p


wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Maternal mortality ratio (modeled estimate, per 100,000 live births)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Maternal mortality ratio (modeled estimate, per 100,000 live births)`,
               name = paste("Maternal mortality ratio (modeled estimate, per 100,000 live births)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Maternal mortality ratio (modeled estimate, per 100,000 live births)"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "Deaths per 100,000 live births"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> mat_mort

```

:::{.panel-tabset}

### [Anemia]{style="font-size:25px"}
```{r}
#| fig-height: 6
#| fig-width: 14 

anemia_w
```
### [Anemia Pregnamt Women]{style="font-size:25px"}
```{r}
#| fig-height: 6
#| fig-width: 14 

anemia_p
```

### [Maternal Mortality]{style="font-size:25px"}
```{r}
#| fig-height: 6
#| fig-width: 14 

mat_mort
```
:::

## Health

```{r health-charts3}

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Mortality rate, under-5 (per 1,000 live births)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Mortality rate, under-5 (per 1,000 live births)`,
               name = paste("Mortality rate, under-5 (per 1,000 live births)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Mortality rate, under-5 (per 1,000 live births)"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "Number per 1000 live births"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> mort_rate

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Immunization, DPT (% of children ages 12-23 months)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Immunization, DPT (% of children ages 12-23 months)`,
               name = paste("Immunization, DPT (% of children ages 12-23 months)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Immunization, DPT"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of children ages 12-23 months"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> imm_dpt

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Immunization, measles (% of children ages 12-23 months)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Immunization, measles (% of children ages 12-23 months)`,
               name = paste("Immunization, measles (% of children ages 12-23 months)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Immunization, measles"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of children ages 12-23 months"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> imm_mea

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Prevalence of stunting, height for age (% of children under 5)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Prevalence of stunting, height for age (% of children under 5)`,
               name = paste("Prevalence of stunting, height for age (% of children under 5)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Stunting children under 5"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of children under 5"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> stunting


```

:::{.panel-tabset}

### Child Mortality
```{r}
#| fig-height: 6
#| fig-width: 14 

mort_rate
```


### Stunting
```{r}
#| fig-height: 6
#| fig-width: 14 

stunting
```
### DPT
```{r}
#| fig-height: 6
#| fig-width: 14 

imm_dpt
```
### Measles
```{r}
#| fig-height: 6
#| fig-width: 14 

imm_mea
```

:::

## Education{.center}

  - There is intrinsic value in having a population that is educated.
  - Education can lead to better outcomes for economic growth.
  - Education can lead to better social mobility.
  - Education of mothers is linked to child development outcomes.
  
```{r charts-edu}
wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Primary completion rate, total (% of relevant age group)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Primary completion rate, total (% of relevant age group)`,
               name = paste("Primary completion rate, total (% of relevant age group)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Primary Completion Rate"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of relevant age group"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> primary_rate

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Adjusted net enrollment rate, primary (% of primary school age children)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Adjusted net enrollment rate, primary (% of primary school age children)`,
               name = paste("Adjusted net enrollment rate, primary (% of primary school age children)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Adjusted Net Enrollement rate"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of primary school age children"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> net_enrollment

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Children out of school, female (% of female primary school age)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Children out of school, female (% of female primary school age)`,
               name = paste("Children out of school, female (% of female primary school age)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Children out of school, female"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of female primary school age"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> female_out_sch

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Children out of school (% of primary school age)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Children out of school (% of primary school age)`,
               name = paste("Children out of school (% of primary school age)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Children out of school"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of primary school age children"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> child_out_sch

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Government expenditure on education, total (% of GDP)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Government expenditure on education, total (% of GDP)`,
               name = paste("Government expenditure on education, total (% of GDP)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Government expenditure on education, total"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of GDP"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> edu_exps

```

## Education

:::{.panel-tabset}

### [Primary Completion]{style="font-size:20px"}

```{r}
#| fig-height: 6
#| fig-width: 14

primary_rate
```


### [Net Enrollment]{style="font-size:20px"}

```{r}
#| fig-height: 6
#| fig-width: 14

net_enrollment
```
### [Out of School]{style="font-size:20px"}

```{r}
#| fig-height: 6
#| fig-width: 14

child_out_sch
```

### [Out of School, female]{style="font-size:20px"}

```{r}
#| fig-height: 6
#| fig-width: 14

female_out_sch
```
### [Government Expenditure]{style="font-size:20px"}

```{r}
#| fig-height: 6
#| fig-width: 14

edu_exps
```
:::

## Tech and Research

```{r}
wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Research and development expenditure (% of GDP)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Research and development expenditure (% of GDP)`,
               name = paste("Research and development expenditure (% of GDP)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Research and development expenditure"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of GDP"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> res_exp

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "High-technology exports (% of manufactured exports)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `High-technology exports (% of manufactured exports)`,
               name = paste("High-technology exports (% of manufactured exports)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "High-technology exports"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of manufactured exports"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> high_exp

```

:::{.panel-tabset}

### [Expenditure on Research and Development]{style="font-size:22px"}

```{r}
#| fig-height: 6
#| fig-width: 14

res_exp

```


### [High Technology Exports]{style="font-size:22px"}
```{r}
#| fig-height: 6
#| fig-width: 14

high_exp

```
:::

## Discussion - Mobility

Credit: Development Data Lab

```{=html}
<iframe width="1400" height="500" src="https://www.devdatalab.org/mobility" title="Quarto Documentation"></iframe>
```

## Discussion - Segregation

Credit: Development Data Lab

```{=html}
<iframe width="1400" height="500" src="https://www.devdatalab.org/segregation" title="Quarto Documentation"></iframe>
```

## Thank you{.center}

**Questions?**