---
title: "India's Socio-Economic Landscape"
author: "Ayush Patel"
date: "September 22, 2023"
subtitle: "Post Independence changes in India"
format: 
  revealjs:
    embed-resources: true
    slide-number: c/t
    width: 1400
    theme: [serif, theme.scss]
execute: 
  echo: false
  warning: false
---


```{r libraries}
library(here) # directories management
library(dplyr) # data wrangling
library(tidyr) # data wrangling
library(highcharter) # interactive data viz

```

```{r load-data}
# read in WB data that is processed and combined.
readr::read_csv(
  "data/WB_socio_economic_inds.csv"
) -> wb_all_ind

# transform WB data in long format.

wb_all_ind[,-c(1,69)]|> 
  pivot_longer(cols = 5:67,
               names_to = "year",
               values_to = "val")|>
  mutate(
    year = as.numeric(year)
  )-> wb_all_ind

# create a vector for comparative countries

names_neighbours_iso3c <- c("BGD","PAK","IND",
                            "CHN","KOR","LKA")

```


## Hello

::::{.columns}

:::{.column width="70%"}
[I am Ayush.]{.fragment fragment-index="1" style="font-size:45px"}


[I am a researcher working at the intersection of data, law, development and economics.]{.fragment fragment-index="2" style="font-size:25px"} 

[I teach Data Science using R at Gokhale Institute of Politics and Economics.]{.fragment fragment-index="3" style="font-size:25px"} 

[I am a [RStudio (Posit) certified tidyverse Instructor.](https://education.rstudio.com/trainers/people/patel+ayush/)]{.fragment fragment-index="4" style="font-size:25px"} 

[I am a Researcher at [Oxford Poverty and Human development Initiative (OPHI)](https://ophi.org.uk/), at the University of Oxford.]{.fragment fragment-index="5" style="font-size:25px"} 
:::

:::{.column width="30%"}

__Reach me__

{{< fa solid envelope >}} [ayush.ap58@gmail.com]{style="font-size:25px"}

{{< fa solid envelope >}} [ayush.patel@gipe.ac.in]{style="font-size:25px"}

:::

::::

## A liberal Constitution

[India adopted liberal constitution that came into force on 26 January 1950.]{.fragment fragment-index="1"}

[   - Universal Adult Franchise.]{.fragment fragment-index="2"}

[   - Equality based on caste, creed and religion]{.fragment fragment-index="3"}

[   - Freedom of speech and movement]{.fragment fragment-index="4"}

[   - Directive Principles of State Policy]{.fragment fragment-index="5"}

[   - Independent Judiciary]{.fragment fragment-index="6"}

>[One could say a right recipe for a harmonious society and growth. We will discuss how Indians and Indian society have changed after independence.]{.fragment fragment-index="7"}

## How are we measuring change?

  - **Education** and **Health**, of various groups, are two broad parameters that signal about a society's wellbeing. Additionally, are also signals for a productive and value generating labour force.
  - We will compare India, using various indicators^[form world bank data], with sub-continental neighbours.
  - We will also investigate, by discussing two papers from [Development Data Lab](https://www.devdatalab.org/), if change has been true for various groups in India.

## Where does India live?

>"India lives in her villages" - M.K. Gandhi

  - How much does this hold true today?
  - Is Urbanization desirable?
  - Has India Urbanized?
  
> "What is the village but a sink of localism, a den of ignorance, narrow-mindedness and communalism..." - B.R.Ambedkar

## Where does India Live?

```{r pop-changes}

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Rural population (% of total population)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Rural population (% of total population)`,
               name = paste("Rural population (% of total population)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Share of Rural Population"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of total population"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> sahre_rural_pop

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Urban population (% of total population)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Urban population (% of total population)`,
               name = paste("Urban population (% of total population)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Share of Urban Population"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of total population"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> sahre_urban_pop

```

:::{.panel-tabset}

### Rural

```{r}
#| fig-height: 6
#| fig-width: 14
sahre_rural_pop
```


### Urban

```{r}
#| fig-height: 6
#| fig-width: 14
sahre_urban_pop
```


:::

## Is India an agrarian economy?{.center}

  - Yes, India was an agrarian economy. Agri,forestry and fishing(1960)-41.7%GDP, Manufacturing(1960)-15%GDP and, Services(1960) - 38.8%GDP.
  - *Is* India an agrarian economy? Difficult to say. Things have changed(Agri,forestry and fishing(2022)-16.6%GDP, Manufacturing(2022)-13%GDP and, Services(2022) - 48.6%GDP).
  - Certainly, not same as 1960s. Is the change universal? Today, how many people are engaged in agriculture?
  
## Is India an agrarian economy?

```{r engaged-agri}
wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Agricultural land (sq. km)"
    )
  )|>
  filter(`Country Code` %in% c("IND","CHN"))|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Agricultural land (sq. km)`,
               name = paste("Agricultural land (sq. km)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Changes in Agriculture Land (sq. Km.)"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "Land in Square Kilometers"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> agri_land_sqm

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Arable land (hectares per person)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Arable land (hectares per person)`,
               name = paste("Arable land (hectares per person)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Arable land (hectares per person)"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "Hectares per person"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> land_per_person

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Agricultural irrigated land (% of total agricultural land)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Agricultural irrigated land (% of total agricultural land)`,
               name = paste("Agricultural irrigated land (% of total agricultural land)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Agricultural irrigated land"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of total agricultural land"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> irrigated_land

wb_all_ind|>
  filter(
    `Indicator Name` %in% c(
      "Employment in agriculture (% of total employment) (modeled ILO estimate)"
    )
  )|>
  filter(`Country Code` %in% names_neighbours_iso3c)|>
  pivot_wider(names_from = `Indicator Name`,
              values_from = val)|>
  hchart(type = "spline",
         hcaes(x = year, y = `Employment in agriculture (% of total employment) (modeled ILO estimate)`,
               name = paste("Employment in agriculture (% of total employment) (modeled ILO estimate)",
                            year),
                  group = `Country Name`))|>
  hc_title(
    text = "Employment in agriculture(modeled ILO estimate)"
  )|>
  hc_caption(
    text = "Data - World Bank"
  )|>
  hc_yAxis(
    title = list(
      text = "% of total employment"
    )
  )|>
   hc_xAxis(
    title = list(
      text = "Year"
    )
  )|>
  highcharter::hc_chart(zoomType = "x") -> agri_employed

```

:::{.panel-tabset}

### Land resource

```{r}
#| fig-height: 6
#| fig-width: 14

agri_land_sqm
```


### Per Capita

```{r}
#| fig-height: 6
#| fig-width: 14

land_per_person
```

### Irrigated land

```{r}
#| fig-height: 6
#| fig-width: 14

irrigated_land
```

### Labour in Agri

```{r}
#| fig-height: 6
#| fig-width: 14

agri_employed
```

:::

## Inefficiencies in Agriculture

  - Today for India, nearly 43% of the total employment is in Agriculture. Even though, value added by agriculture to GDP is ~16%.
  - China, that has a comparable population to India, requires a little more than 3 times the area of agriculture land to support itself. This is despite the fact that yield per hectare in China is higher compared to India^[[see1](https://ageconsearch.umn.edu/record/7510/files/edc87-03.pdf),[see2](https://www.nationmaster.com/country-info/compare/China/India/Agriculture),[see3](https://www.cambridge.org/core/journals/journal-of-asian-studies/article/abs/chinese-and-indian-agriculture-a-broad-comparison-of-recent-policy-and-performance/49317DFE78554C23AC3467F604AF009B)].
  - India has a lower share of irrigated land compared to Bangladesh and Pakistan.